NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-10-30 conclusions.tex
small modification

We calculated the next-to-leading order QCD and electroweak corrections to these three processes for a set
of realistic fiducial cuts. Particular
emphasis has been put on the up to now unknown electroweak corrections as well as the combination of QCD and
electroweak corrections with the aim of producing the most precise prediction possible within the Standard Model.
As expected, we found the QCD corrections to be large and dominant compared to the electroweak corrections when 
calculating the corrections to the total cross sections. QCD corrections are particular large for these processes due to new
channels opening up at NLO but can effectively be reduced by applying a jet veto. Electroweak corrections
lead to moderate corrections to the total cross section of up to $4.4\%$ for the $\gamma\gamma \ell^{+}\ell^{-}$ 
process. However, in the high energy tail of differential distributions the electroweak corrections become increasingly important
and can lead to corrections of up to $30 \%$. Electroweak corrections become important in the same regions where one
also expects increasing effects of higher dimensional operators. The precise determination of limits on higher dimensional 
operators therefore requires the inclusion of higher order correction of both QCD as well as of the electroweak interaction.
We also compared the two possibilities of combining QCD with electroweak corrections, namely either in an additive or
in a multiplicative way. One expects that the difference between the two schemes is small as they can be seen as an estimation
of neglected higher order contributions. We found that although this is true on the level of total cross sections there can be 
regions in phase space where the leading order contribution vanishes and therefore the k-factor become infinitely large. 
For those kinematical edges we observe a breakdown of the multiplicative scheme whereas the additive scheme provides
a reliable estimation of the higher order uncertainties throughout the whole phase space.

>>>>

We calculated the next-to-leading order QCD and electroweak corrections to these three processes for a set
of realistic fiducial cuts. Particular
emphasis has been put on the up to now unknown electroweak corrections as well as the combination of QCD and
electroweak corrections with the aim of producing the most precise prediction possible within the Standard Model.
As expected, we found the QCD corrections to be large and dominant compared to the electroweak corrections when 
calculating the corrections to the total cross sections. QCD corrections are particular large for these processes due to new
channels opening up at NLO but can effectively be reduced by applying a jet veto. Electroweak corrections
lead to moderate corrections to the total cross section of up to $4.4\%$ for the $\gamma\gamma \ell^{+}\ell^{-}$ 
process. However, in the high energy tail of differential distributions the electroweak corrections become increasingly important
and can lead to corrections of up to $30 \%$. Electroweak corrections become important in the same regions where one
also expects increasing effects of higher dimensional operators. The precise determination of limits on higher dimensional 
operators therefore requires the inclusion of higher order correction of both QCD as well as of the electroweak interaction.

We also compared the two possibilities of combining QCD with electroweak corrections, namely either in an additive or
in a multiplicative way. One expects that the difference between the two schemes is small as they can be seen as an estimation
of neglected higher order contributions. We found that although this is true on the level of total cross sections there can be 
regions in phase space where the leading order contribution vanishes and therefore one or both $K$-factors become infinitely large. 
For those kinematical edges we observe a breakdown of the multiplicative scheme whereas the additive scheme provides
a reliable estimation of the higher order uncertainties throughout the whole phase space.
